Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/introduction.tex
edits

Of course, the problem of finding compressed or small networks is not new.
Existing techniques typically aim make a pre-trained neural network smaller
\cite{something1,something2} by taking one of two approaches:  either by
applying quantization \cite{quant} or code compilation~\cite{something}
techniques that can be applied blindly to any network, or by analyzing the
structure of the network and systematically pruning
connections~\cite{han2015deepcompression,Cun} or neurons~\cite{XXX}
based on some loss function.  Although these techniques can substantially
reduce model size, they have several drawbacks.  First, they often negatively
impact model quality.  Second, they can (surprisingly) negatively impact
inference time as they transform dense matrix operations into sparse ones,
which can be substantially slower to execute on modern hardware
\cite{something}, especially GPUs which do not efficiently support sparse
linear algebra.  Third, these techniques generally start by optimizing a
particular architecture for prediction performance, and then, as a post-
processing step, applying compression  to generate a smaller model that meets the
resource constraints of the deployment setting.  Because the network
architecture is essentially fixed during this post-processing,   model architectures
that work better in small settings may be missed -- this is especially true in
large networks like many-layered CNNs,  where it is infeasible to try explore
even a small fraction of possible network configurations.

@@

The remaining of this paper is organized as follows. In section
\ref{sec:relatedwork} we discuss the related work. In section
\ref{sec:approach}, we introduce our approach ShrinkNets, followed by the
practical considerations we implemented to make it work in section
\ref{sec:impl}. Then, we evaluate the approach in section \ref{sec:evaluation}
and conclude the paper in section \ref{sec:conclusions}.

>>>>

Of course, the problem of finding compressed or small networks is not new.
Existing techniques typically aim make a pre-trained neural network smaller
by taking one of two approaches:  either by
applying quantization \cite{quant} or code compilation~\cite{ma2016compilation}
techniques that can be applied blindly to any network, or by analyzing the
structure of the network and systematically pruning
connections or neurons~\cite{han2015deepcompression,Cun}
based on some loss function.  Although these techniques can substantially
reduce model size, they have several drawbacks.  First, they often negatively
impact model quality.  Second, they can (surprisingly) negatively impact
inference time as they transform dense matrix operations into sparse ones,
which can be substantially slower to execute on modern hardware
\cite{han2015deepcompression}, especially GPUs which do not efficiently support sparse
linear algebra.  Third, these techniques generally start by optimizing a
particular architecture for prediction performance, and then, as a post-
processing step, applying compression  to generate a smaller model that meets the
resource constraints of the deployment setting.  Because the network
architecture is essentially fixed during this post-processing,   model architectures
that work better in small settings may be missed -- this is especially true in
large networks like many-layered CNNs,  where it is infeasible to try explore
even a small fraction of possible network configurations.

@@

% The remaining of this paper is organized as follows. In section
% \ref{sec:relatedwork} we discuss the related work. In section
% \ref{sec:approach}, we introduce our approach ShrinkNets, followed by the
% practical considerations we implemented to make it work in section
% \ref{sec:impl}. Then, we evaluate the approach in section \ref{sec:evaluation}
% and conclude the paper in section \ref{sec:conclusions}.
